\name: A Non-Parametric, Hierarchical \\ Wavelength-Calibration Model for a Precision Spectrograph

### 2020-05-25 paper/paper.tex
New Figures and Captions

\begin{figure*}[h]
\centering
\includegraphics[width=\textwidth]{Figures/methodCartoon.pdf}
\caption{A cartoon representation of the \name\ method, as described in Section \ref{sec:method}.  We enlarge variations in measured line position, changes in calibration space, and interpolation deviations for clarity.  In step one, dimensionality reduction and denoising, the complete set of line positions for all exposures is analyzed to return a set of basis vectors, $g_n$, which represent different ways the spectrograph calibration changes, and spans the possible calibration space of the spectrograph.  In step two, \name\ interpolates the amplitudes of each basis vector, $a_n,k$, to return the calibration state for a specific exposure, returned as a set of de-noised calibration lines.  The assigned wavelengths of these de-noised line positions are then interpolated onto other pixels in step three to construct a full wavelength model.}
\label{fig:testHists}
\end{figure*}

@@

\begin{figure}[h]
\centering
\includegraphics[width=.5\textwidth]{Figures/all_results.pdf}
\caption{Difference in predicted and theoretical wavelengths for the wavelength calibration tests described in Section \ref{sec:tests}.  The standard deviation of the residuals for each test is given in the top-right corner in each method's corresponding color.}
\label{fig:testHists}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.5\textwidth]{Figures/lineResids2D_col.png}
%\includegraphics[width=0.5\textwidth]{Figures/lineResids2D_col.pdf}
\caption{Residuals for a single LFC exposure plotted with respect to detector position (as defined by echelle order and x-pixel) for various wavelength calibration methods.  Each line is colored by the difference between the predicted wavelength and the theoretical wavelength for each line, given in units of $\mps$.  Residuals to a classic, polynomial fit are shown in the top plot.  The center plot shows residuals to an interpolated wavelength solution.  The bottom plot shows residuals when a ThAr wavelength model generated by \name\ is interpolated onto LFC line positions.  The positions of ThAr lines are over-plotted in black.}
\label{fig:resid2d}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.5\textwidth]{Figures/lineDensity.png}
\caption{Comparison of polynomial-fit and interpolated wavelength solutions using either just ThAr lines or LFC lines.  For a subset of one order, the difference between the assigned and model wavelengths for each LFC line is plotted with respect to pixel.  The large residuals between two widely-spaced ThAr lines when implementing an interpolated wavelength solution with just ThAr lines (blue curve) extends out of frame.}
\label{fig:waveResids}
\end{figure}

@@

\begin{figure*}[t]
\centering
\includegraphics[width=\textwidth]{Figures/pcsLfc9.png}
%\includegraphics[width=\textwidth]{Figures/pcsLfc6.pdf}
\caption{The first nine principal components constructed using LFC lines.  Each line is plotted according to its echelle order and x-pixel and colored by the value of the principal component for that line.}
\label{fig:pcLfc}
\end{figure*}

@@

\begin{figure}[t]
\centering
\includegraphics[width=.5\textwidth]{Figures/kvals_all.pdf}
\caption{Spread in residuals of returned wavelengths for different values of $K$.  There is a dotted, vertical line at $K=6$, our chosen $K$ value.  The dotted, horizontal line is the RMS for $K=6$.}
\label{fig:kvals}
\end{figure}

@@

\begin{figure*}[h!]
\centering
\includegraphics[width=0.56\textwidth]{Figures/pcA_lfc.png}
\includegraphics[width=0.42\textwidth]{Figures/pcAs_byDay.png}
\caption{Amplitude of the first two principal components shown as a function of time (left) or fraction of a day (right).  The top row of plots shows the amplitudes for the first principal component while the bottom row shows the amplitudes for the second principal component.  Points mark the times at which we have calibration data.  Lines show the result of a linear interpolation.  In the right plot, the principal component amplitudes have been artificially offset by the median amplitude for each day so that all days are roughly on the same scale.  Here, points are colored by the MJD of each exposure.}
\label{fig:nightlyVariation}
\end{figure*}

@@

\begin{figure*}[h]
\centering
\includegraphics[width=\textwidth]{Figures/intpx_tests.png}
\caption{Residuals from different interpolation schemes over pixels in a single order.  ThAr lines, shown as black circles, are used to construct a wavelength solution that is then evaluated at each LFC line, shown as black lines.  The residuals of each wavelength solution for a subset of the order is shown on the left.  Histograms of the residuals for each method for the complete order is shown on the right.  Here, the y-axis is zoomed in to show the shape of each histogram more clearly.  Note: there is a blended ThAr line at approximately pixel 5300, the last ThAr line plotted.}
\label{fig:xinterp}
\end{figure*}

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.5\textwidth]{Figures/lfcDensityTest.pdf}
\caption{Scatter in residuals as a function of spacing between lines.  The residuals are the difference between the\name\ wavelengths and each line's theoretical wavelength in units of $\mps$.  The average line spacing is calculated using the average distance between LFC lines across its wavelength range.}
\label{fig:density}
\end{figure}

>>>>

\begin{figure*}[h]
\centering
\includegraphics[width=\textwidth]{Figures/methodCartoon.pdf}
\caption{A cartoon representation of the \name\ method, as described in Section \ref{sec:method}.  We enlarge variations in measured line position, changes in calibration space, and interpolation deviations for clarity.  In step one, dimensionality reduction and denoising (\textsection \ref{sec:denoising}), the complete set of line positions for all exposures is analyzed to return a set of basis vectors, $g_n$, which represent different ways the spectrograph calibration changes.  These basis vectors span the possible calibration space of the spectrograph.  In step two (\textsection \ref{sec:interp_time}), \name\ interpolates the amplitudes of each basis vector, $a_n,k$, to return the calibration state for a specific science exposure, returned as a set of de-noised calibration lines.  The assigned wavelengths of these de-noised line positions are then interpolated onto other pixels in step three (\textsection \ref{sec:interp_wsol}) to construct a full wavelength model that returns wavelength as a function of detector position $x$ and echelle order $m$.}
\label{fig:testHists}
\end{figure*}

@@

\begin{figure}[h]
\centering
\includegraphics[width=.5\textwidth]{Figures/all_results.pdf}
\caption{Difference in predicted and theoretical wavelengths for the wavelength calibration tests described in Section \ref{sec:tests}.  The standard deviation of the per line residuals for each test, or the per line RMS as defined in Equation \ref{eq:rms} is given in the top-right corner in each method's corresponding color.  \name\ returns the smallest spread in residuals.}
\label{fig:testHists}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.5\textwidth]{Figures/lineResids2D_col.png}
%\includegraphics[width=0.5\textwidth]{Figures/lineResids2D_col.pdf}
\caption{Residuals for a single LFC exposure plotted with respect to detector position (as defined by echelle order and x-pixel) for parametric and non-parametric wavelength calibration methods.  Each line is colored by the difference between the predicted wavelength and the theoretical wavelength for each line, given in units of $\mps$.  Residuals to a classic, polynomial fit are shown in the top plot.  The bottom plot shows residuals to an interpolated wavelength solution.  High-order structure, i.e. vertical stripes and patchiness, is apparent in the residuals to a polynomial wavelength solution, which assumes smoothness.  The increased flexibility of the interpolated wavelength solution can account for this high-order structure, resulting in much smaller residuals with less spatial coherence.}
\label{fig:resid2d}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=\textwidth]{Figures/lineDensity.png}
\caption{Residuals when using ThAr lines to predict wavelengths for LFC lines.  \textbf{Right}: residuals for a single LFC exposure plotted with respect to detector position as in Figure \ref{fig:resid2d}.  Each line is colored by the difference between the predicted wavelength and the theoretical wavelength for each line, given in units of $\mps$.  The positions of ThAr lines are over-plotted in yellow.  In general, residuals are greater between ThAr lines with greater separation.
\textbf{Left}: Comparison of polynomial-fit and interpolated wavelength solutions using either just ThAr lines or LFC lines.  For a subset of echelle order 94, the difference in Angstroms between the assigned and model wavelengths for each LFC line is plotted with respect to pixel.  The large residuals between two widely-spaced ThAr lines when implementing an interpolated wavelength solution with just ThAr lines (orange curve) extends out of frame.  Note how the shape of the residuals from a polynomial fit are similar whether using ThAr lines or LFC lines, suggesting that little is added with the denser LFC lines.  The LFC lines only serve to make the residuals more centered around zero.  A PCHIP interpolated wavelength model guided by LFC lines returns the smallest residuals.}
\label{fig:waveResids}
\end{figure}

@@

\begin{figure*}[t]
\centering
\includegraphics[width=\textwidth]{Figures/pcsLfc9.png}
%\includegraphics[width=\textwidth]{Figures/pcsLfc6.pdf}
\caption{\textbf{Top}:  The fiducial calibration of the spectrograph, i.e. the mean line positions for each line throughout the epoch of stability.  The following plots show the first nine principal components constructed using LFC lines.  These principal components represent the basis vectors along which the calibration of the spectrograph can deviate from the fiducial calibration.  For each basis vector, each calibration line is plotted according to its echelle order and x-pixel and colored by the value of the basis vector for that line.  Principal components beyond the sixth one become steadily more dominated by noise.}
\label{fig:pcLfc}
\end{figure*}

@@

\begin{figure}[t]
\centering
\includegraphics[width=.5\textwidth]{Figures/kvals_all.pdf}
\caption{Per line RMS of returned wavelength models for different values of $K$.  Per line RMS is defined in Equation \ref{eg:rms}.  There is a dotted, vertical line at $K=6$, our chosen $K$ value.  The dotted, horizontal line is the RMS for $K=6$.  The improvement at around $K=6$ plateaus.}
\label{fig:kvals}
\end{figure}

@@

\begin{figure*}[h!]
\centering
\includegraphics[width=\textwidth]{Figures/pcAs_byDay.png}
\caption{Amplitude of the first two principal components shown as a function of time (left) or hour from midnight (right).  The top row of plots shows the amplitudes for the first principal component while the bottom row shows the amplitudes for the second principal component.  Points mark the times at which calibration exposures were taken.  Lines show the result of a linear interpolation.  In the right plot, the principal component amplitudes have been artificially offset by the median amplitude for each night.  All days are therefore roughly on the same scale, but the y-axis is different from the left plots.  In the right column, points are colored by the time of each exposure.}
\label{fig:nightlyVariation}
\end{figure*}

@@

\begin{figure*}[h]
\centering
\includegraphics[width=\textwidth]{Figures/intpx_tests.png}
\caption{Residuals from different interpolation schemes over pixels in echelle order 100.  ThAr lines, shown as blue circles, are used to construct a wavelength solution that is then evaluated at each LFC line, shown as blue lines.  The residuals of each wavelength solution for a subset of the order is shown on the left.  Histograms of the residuals for each method for the complete order is shown on the right.  Here, the y-axis is zoomed in to show the shape of each histogram more clearly.  Note: there is a blended ThAr line at approximately pixel 5300, the last ThAr line plotted.}
\label{fig:xinterp}
\end{figure*}

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.5\textwidth]{Figures/lfcDensityTest.pdf}
\caption{Per line RMS as a function of spacing between lines in units of resolution element.  The average line spacing is calculated using the average distance between LFC lines across its wavelength range.}
\label{fig:density}
\end{figure}
